---
title: "A Landmark-based Framework for Image Comparison
in the Presence of Various Geometric Misalignments - Power Computation Polygon"
author: "Anik Roy, Sagar Ghosh, Partha Sarathi Mukherjee"
date: "2026-03-28"
output:
  pdf_document: default
  word_document: default
  html_document: default
# header-includes:
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

\textbf{Description: This code snippet intakes two Polygon images and outputs the power of the test described in Section $4.2$ of the manuscript, where the test treats the first image as null $(H_0)$ and the second image as alternate $(H_1)$. More precisely, this particular demonstration computes the power of the test $g_{P,0}$ vs $g_{P,2}^{(H_1)}$}. 

```{r, echo=TRUE, cache=TRUE, results='hide'}
#if (!requireNamespace("BiocManager", quietly = TRUE))
#  install.packages("BiocManager")

#BiocManager::install("EBImage")


library(EBImage)
library(raster)
library(sp)
library(magick)
library(OpenImageR)
library(foreach)
library(doParallel)
library(DRIP)
library(twosamples)
library(OpenImageR)
library(magic)
library(pracma)
library(jpeg)
library(SAFARI)
#library(imager)
```

```{r, echo=TRUE, cache=TRUE}
# 1. Euclidean Invariant Metric
  
  Centering_matrix=function(k){
    C=matrix(0,nrow=k,ncol = k)
    for(i in 1:k){
      for(j in 1:k){
        if(i==j){
          C[i,j]=(k-1)/k
        }
        else{
          C[i,j]=(-1)/k
        }
      }
    }
    return(C)
  }
  
  # 2. Frobeneous Norm
  
  frob_norm=function(mat){
    a=nrow(mat)
    b=ncol(mat)
    d=0
    for(i in 1:a){
      for(j in 1:b){
        d=d+mat[i,j]^2
      }
    }
    return(sqrt(d))
  }
  
  # 3. TRS invariant metric
  
  TRS=function(X1,X2){
    k=nrow(X1)
    C=Centering_matrix(k)
    Z1=(C%*%X1)
    Z2=(C%*%X2)
    T1=(Z1%*%t(Z1))
    T2=(Z2%*%t(Z2))
    dist_matrix=(1/(frob_norm(T1)))*T1 - (1/(frob_norm(T2)))*T2
    dist=max(abs((dist_matrix)))
    return(dist)
  }
  
  # 3.1 TRS Local Change Detection
  TRS_local <- function(X1, X2) {
    k <- nrow(X1)
    C <- Centering_matrix(k)
    
    Z1 <- C %*% X1
    Z2 <- C %*% X2
    
    T1 <- Z1 %*% t(Z1)
    T2 <- Z2 %*% t(Z2)
    
    dist_matrix <- (1 / frob_norm(T1)) * T1 - (1 / frob_norm(T2)) * T2
    
    # Maximum absolute change
    dist <- max(abs(dist_matrix))
    
    # Indices where maximum change occurs
    idx <- which(abs(dist_matrix) == dist, arr.ind = TRUE)
    
    # Indices of X1 involved (row/column indices map directly to rows of X1)
    X1_indices <- unique(as.vector(idx))
    
    return(list(
      dist = dist,
      dist_matrix = dist_matrix,
      max_change_indices = idx,      # (i, j) pairs in the matrix
      X1_indices = X1_indices        # which rows of X1 correspond
    ))
  }
  
  
  # 4. Boundary curve estimation
  
  sample_edge=function(X,h_n){
    #X: Image matrix
    #X=readJPEG("2004-1c1.jpg")[,,1]
    est_img=JPLLK_surface(X,3,plot = F)$fitted
    e=stepEdge(est_img,h_n,(qnorm(0.999,0,1)*JPLLK_surface(est_img,3)$sigma)
               ,degree=0,plot = F)
    e[1,]=0
    e[2,]=0
    e[,1]=0
    e[,2]=0
    e[nrow(X),]=0
    e[nrow(X)-1,]=0
    e[,ncol(X)]=0
    e[,ncol(X)-1]=0
    for(k in 1:nrow(X)){
      for(l in 1:ncol(X)){
        if(k>2 && l>2 && k< (nrow(X)-1) && l< (ncol(X)-1) && e[k,l]==1 &&  
           sum(e[(k-1):(k+1),(l-1):(l+1)])<=4){
          e[k,l]=0
        }
        
      }
    }
    e[1,]=0
    e[2,]=0
    e[,1]=0
    e[,2]=0
    e[nrow(X),]=0
    e[nrow(X)-1,]=0
    e[,ncol(X)]=0
    e[,ncol(X)-1]=0
    for(k in 1:nrow(X)){
      for(l in 1:ncol(X)){
        if(k>2 && l>2 && k< (nrow(X)-1) && l< (ncol(X)-1) && e[k,l]==1 &&  
           sum(e[(k-1):(k+1),(l-1):(l+1)])<=3){
          e[k,l]=0
        }
        
      }
    }
    e[1,]=0
    e[2,]=0
    e[,1]=0
    e[,2]=0
    e[nrow(X),]=0
    e[nrow(X)-1,]=0
    e[,ncol(X)]=0
    e[,ncol(X)-1]=0
    for(k in 1:nrow(X)){
      for(l in 1:ncol(X)){
        if(k>2 && l>2 && k< (nrow(X)-1) && l< (ncol(X)-1) && e[k,l]==1 &&  
           sum(e[(k-1):(k+1),(l-1):(l+1)])<=3){
          e[k,l]=0
        }
        
      }
    }
    P=as.matrix(which(e==1,arr.ind = T))
    #plot(P)
    return(P)
  }
  
  #5. Landmark Point Selection
  
  choose_landmarks <- function(P,
                               center = NULL,
                               K = NULL,
                               dtheta = NULL,
                               angle_start = 0,
                               tol = 1.0,
                               max_tol = 5.0) {
    stopifnot(is.matrix(P) || is.data.frame(P))
    P <- as.matrix(P)
    stopifnot(ncol(P) == 2)
    colnames(P) <- c("x", "y")
    
    if (is.null(center)) center <- colMeans(P)
    stopifnot(length(center) == 2, is.finite(center[1]), is.finite(center[2]))
    
    if (is.null(K) && is.null(dtheta))
      stop("Provide either K or dtheta (degrees).")
    if (!is.null(dtheta)) {
      stopifnot(dtheta > 0)
      dtheta_rad <- dtheta * pi / 180
      K <- max(1L, round(2 * pi / dtheta_rad))
    }
    stopifnot(K >= 1)
    
    # Anticlockwise target angles
    angles <- angle_start + 2 * pi * (0:(K - 1)) / K
    
    # Vectors from center to each edge point
    V <- sweep(P, 2, center, FUN = "-")         # n x 2
    n <- nrow(P)
    
    pick_for_angle <- function(theta) {
      # Direction of the ray
      d <- c(cos(theta), sin(theta))
      # Perpendicular (left normal) to measure distance from the ray
      nperp <- c(-sin(theta), cos(theta))
      
      # Longitudinal (along-ray) and lateral (perpendicular) components
      t <- V %*% d          # projection length along the ray
      s <- V %*% nperp      # signed perpendicular distance to the ray
      
      # Expand tolerance until we find candidates, 
      #preferring the farthest along the ray
      tol_k <- tol
      chosen <- NA_integer_
      while (is.na(chosen) && tol_k <= max_tol) {
        cand <- which(abs(s) <= tol_k & t > 0)
        if (length(cand) > 0) {
          chosen <- cand[which.max(t[cand])]   # farthest hit along this ray
        } else {
          tol_k <- tol_k * 1.5
        }
      }
      
      # If still nothing, fall back to nearest-angle point 
      #(dense edges usually make this rare)
      if (is.na(chosen)) {
        phi <- atan2(V[, 2], V[, 1])
        adiff <- abs(atan2(sin(phi - theta), cos(phi - theta)))  # circular difference
        chosen <- which.min(adiff)
      }
      chosen
    }
    
    idx <- vapply(angles, pick_for_angle, integer(1))
    L <- P[idx, , drop = FALSE]
    rownames(L) <- NULL
    attr(L, "center") <- center
    attr(L, "angles") <- angles
    attr(L, "indices") <- idx
    L
  }
  
  plot_landmarks <- function(P, L, center = attr(L, "center")) {
    plot(P, asp = 1, pch = 16, cex = 0.4, col = "grey70",
         xlab = "x", ylab = "y", main = "Landmarks by Ray Casting")
    points(L, pch = 19)
    segments(center[1], center[2], L[, 1], L[, 2], lty = 3)
    points(center[1], center[2], pch = 4, lwd = 2, cex = 1.2)
    text(L, labels = seq_len(nrow(L)), pos = 3, cex = 0.7)
  }

```


## Null and Alternate Images
\textbf{Null Ellipse: $g_{P,0}$, Alternate Ellipse: $g_{P,2}^{(H_1)}$}
```{r, echo=TRUE, cache=TRUE}
convex_polygon_image <- function(m=300, n=300, R=0.9, H=64) {
  set.seed(7)
  th <- runif(H, 0, 2*pi)
  # normals
  N <- cbind(cos(th), sin(th))
  # random radii around R (keep positive & bounded to remain convex and closed)
  r <- R * (0.7 + 0.3*runif(H))
  b <- r  # since support in direction N_k is r_k

  xs <- seq(-1, 1, length.out = n)
  ys <- seq(-1, 1, length.out = m)
  XX <- matrix(rep(xs, each = m), nrow = m)
  YY <- matrix(rep(ys, times = n), nrow = m)

  img <- matrix(1L, m, n)
  for (k in seq_len(H)) {
    img[ (N[k,1]*XX + N[k,2]*YY) > b[k] ] <- 0L
  }
  img
}
x <- convex_polygon_image(256, 256, R=0.52, H=50)

nimg <- x + matrix(rnorm(nrow(x)*ncol(x),0,0.01),nrow=nrow(x),ncol=ncol(x))
image(nimg ,useRaster=TRUE,axes=FALSE,col = gray(0:256 / 256), asp=1)

```

```{r, echo=TRUE, cache=TRUE}

# # Alternative image
x_1 <- translation(convex_polygon_image(256, 256, R=0.52, H=20)
                   ,shift_rows = 3,shift_cols = 2)


nimg1 <- x_1 + matrix(rnorm(nrow(x)*ncol(x),0,0.01),nrow=nrow(x),ncol=ncol(x))
image(nimg1 ,useRaster=TRUE,axes=FALSE,col = gray(0:256 / 256), asp=1)

```

## Empirical Power Computation
```{r, echo=TRUE, cache=TRUE}
h=2
library(DRIP)
nimg_1 <- x+matrix(rnorm(nrow(x)*ncol(x),0,0.01),nrow=nrow(x),ncol=ncol(x)) 
nimg_2 <- x_1+matrix(rnorm(nrow(x)*ncol(x),0,0.01),nrow=nrow(x),ncol=ncol(x)) 
est_img_1 <- JPLLK_surface(x,3,plot = F)$fitted             
# Jump preserving estimate of image 1
est_img_2 <- JPLLK_surface(x_1,3,plot = F)$fitted          
# Jump preserving estimate of image 2
edge_1 <- stepEdge(est_img_1,h,(qnorm(0.999,0,1)*JPLLK_surface(est_img_1,3)$sigma)
                   ,degree=0,plot = F)
edge_2 <- stepEdge(est_img_2,h,(qnorm(0.999,0,1)*JPLLK_surface(est_img_2,3)$sigma)
                   ,degree=0,plot = F)
resid1 <- nimg_1-est_img_1
resid2 <- nimg_2-est_img_2

sigma1_hat <- JPLLK_surface(x,3,plot = F)$sigma
sigma2_hat <- JPLLK_surface(x_1,3,plot = F)$sigma

#------------Generate null distribution ---------#
epoch = 100
TRS_dist_H0=array(0,epoch)
for(q in 1:epoch){
  set.seed(2025+q)
  nimg_1.star <-  est_img_1 + matrix(rnorm(nrow(x)*ncol(x),0,sigma1_hat)
                                     ,nrow=nrow(x),ncol=ncol(x))
  nimg_2.star <-  translation(rotateImage(est_img_1,runif(1,0,20) 
                                          , threads = 1)
                              ,shift_rows = sample(1:10,1)
                              ,shift_cols = sample(1:10,1))
                         + matrix(rnorm(nrow(x)*ncol(x),0,sigma2_hat)
                                  ,nrow=nrow(x),ncol=ncol(x))

  P1  <- sample_edge(nimg_1.star,h)
  L1  <- choose_landmarks(P1, dtheta = 1)
  P2  <- sample_edge(nimg_2.star,h)
  L2  <- choose_landmarks(P2, dtheta = 1)
  TRS_dist_H0[q] <- TRS(L1,L2)
  
}
cut_off <- quantile(TRS_dist_H0,0.95)


TRS_dist_H1 <- array(0,epoch)
for(q in 1:epoch){

  set.seed(2025+q)
  nimg_1.star <-  est_img_2 + matrix(rnorm(nrow(x)*ncol(x),0,sigma1_hat)
                                     ,nrow=nrow(x),ncol=ncol(x))
  nimg_2.star <-  translation(rotateImage(est_img_1,runif(1,0,20) 
                                          , threads = 1)
                              ,shift_rows = sample(1:10,1)
                              ,shift_cols = sample(1:10,1))
  + matrix(rnorm(nrow(x)*ncol(x),0,sigma2_hat),nrow=nrow(x)
           ,ncol=ncol(x))

  P1  <- sample_edge(nimg_1.star,h)
  L1  <- choose_landmarks(P1, dtheta = 1)
  P2  <- sample_edge(nimg_2.star,h)
  L2  <- choose_landmarks(P2, dtheta = 1)
  TRS_dist_H1[q] <- TRS(L1,L2)

}
power <- sum(TRS_dist_H1>cut_off)/epoch

print(power)



```